%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{hyperref}
\usepackage{xcolor} % Already used for section color
\hypersetup{
  colorlinks=true,
  urlcolor=black,      % Makes hyperlinks blue (you can change this)
  linkcolor=black,    % For internal links like TOC (not used here)
  citecolor=black     % For citations (not used here)
}


\linespread{0.95}

% Set applicant's personal data for header
\name{Yair Ziv}
\address{Petah Tikva, Israel \linebreak \href{tel:+(972) 52-536-9906}{+(972) 52-536-9906}}
\contacts{\href{mailto:zivyair06@gmail.com}{zivyair06@gmail.com} \linebreak \href{https://www.linkedin.com/in/yair-ziv}{LinkedIn} \linebreak \href{https://github.com/Yair-Ziv}{GitHub}}

\begin{document}

	% Print the header
	\makeheader
	
	\begin{cvsection}{Profile}
		Backend engineer with 4+ years of experience building scalable systems in Kotlin and .NET. Known for delivering clean architecture, reliable infrastructure, and production-ready solutions in fast-paced environments. I thrive on ownership, simplifying complexity, and push for impact — in code, teams, and outcomes.
	\end{cvsection}
	% Print the content
	\begin{cvsection}{Professional Experience}
		\begin{cvsubsection}{Backend Developer}{Xpand}{2024 - Present}
			\begin{itemize}
				\item Developed backend adapters for B2B autonomous retail systems; enabling smooth client integration and \linebreak real-time order and product syncing.
				\item Revamped orchestration service to streamline workflows, improving reliability and simplifying debugging and monitoring.
				\item Engineered production-grade backend systems in Kotlin (Spring Boot) and C\# (.NET Core), leveraging MQs for real-time operations.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer}{Xpand}{2021 – 2023}
			\begin{itemize}
				\item Built robotics software in Python and C\#, combining GPU-accelerated OpenCV with real-time control logic.
				\item Helped evolve a prototype into a stable, production-ready robotics platform.
				\item Developed backend services using PostgreSQL and .NET, improving reliability and system visibility.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Developer Intern}{Check Point Software Technologies}{2018 – 2019}
			\begin{itemize}
			  \item Built internal ASP.NET tools backed by MSSQL to streamline issue tracking between support and R\&D, reducing resolution time and improving handoff quality.
			  \item Created automated dashboards to surface real-time team metrics and support data-driven decisions by \linebreak engineering leads.
			\end{itemize}
		  \end{cvsubsection}
		  
	\end{cvsection}
	
	\begin{cvsection}{Military Service}
		\begin{cvsubsection}{Shooting Instructor}{IDF}{2019 - 2021}
			Led the Border Protection Corps’ shooting instructor team as a sergeant, improving marksmanship training standards across the unit. Earned two certificates of excellence for leadership and performance.
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{High School Diploma}{Tichonet Alterman}{2012 - 2018}
			Majored in Computer Science, Physics and Mechanical Control.
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Software Team Lead}{\href{https://www.firstinspires.org/robotics/frc/what-is-first-robotics-competition}{FIRST Robotics Competition}}{2016 - 2018}	
			Served as the team’s programming lead, developing real-time control software that achieved top placements in national competitions. Implemented advanced robotics systems using OpenCV for image processing and \linebreak closed-loop control for autonomous navigation and interaction.
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Additional Courses}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \href{https://www.edx.org/cs50}{CS50: Introduction to Computer Science \tiny{ - Harvard University}}
				\item \href{https://www.udemy.com/course/docker-and-kubernetes-the-complete-guide/}{Docker and Kubernetes: The Complete Guide \tiny{ - Stephen Grider}}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Programming Languages:} C\#, Kotlin, Python
				\item \textbf{Frameworks:} .NET Core, Spring Boot
				\item \textbf{Technologies:} SQL (PostgreSQL, MySql), NoSql (Redis, MongoDB), MQ (Kafka, ZeroMq), \linebreak Containerization (Docker, Kubernetes), CI/CD (Git, GitHub Actions, Jenkins), Cloud (AWS, Azure)
				\item \textbf{Languages:} Hebrew - Native, English - Fluent
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}